### 2012-03-19 paper.tex
Microscopic update

\section{Results}
An oscillation measurement is performed by mounting a sample in the setup directly after cluster deposition and anodic bonding. Initially a light-off CO-oxidation measurement is performed where the temperature is increased at 3\,$^\circ$C/min until the sample ignites and achieves full conversion of CO to CO$_2$. At CO:O$_2$ ratio of $\sim0.08$ and a geometrical Pt coverage of $\sim0.1\%$ light-off occurs at approximately 180\,$^\circ$C. The temperature ramp is typically continued up to 260\,$^\circ$C whereafter the temperature is decreased at the same rate as the heating ramp. After the initial light-off the sample is cooled to room temperature. When at room temperature the temperature is again increased at 3\,$^\circ$C/min until sustained oscillations occur. A typical initial treatment is seen in Figure~\ref{fgr:initial_treatment} where both the symmetrical light-off ramp and the subsequent increase in temperature to achieve sustained oscillations is seen. Often the sample will show oscillations either directly upon light-off or on the falling temperature ramp.
\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{initial_treatment.png}
  \caption{A typical example of the initial treatment of a new sample. After performing a light-off ramp where oscillations can been seen the temperature is increased to a constant value where sustained oscillations take place. The non-zero value of CO during high conversion periods is consistent with the expected QMS background signals from CO$_2$ and O$_2$.}
  \label{fgr:initial_treatment}
\end{figure}
Nanoparticles with sizes ranging from 3\,nm to 9\,nm have been tested but 3\,nm particles with a geometrical coverage of 0.1\% of the reactor area gave the most stable oscillations. No consistent dependency on oscillation frequency and duty cycle was found that could be attributed to the size of the particles.

>>>>

\section{Results}
An oscillation measurement is performed by mounting a sample in the setup directly after cluster deposition and anodic bonding. Initially a light-off CO-oxidation measurement is performed (shown in Figure~\ref{fgr:initial_treatment}) where the temperature is increased at 3\,$^\circ$C/min until the sample ignites and achieves full conversion of CO to CO$_2$. At CO:O$_2$ ratio of $\sim0.08$ and a geometrical Pt coverage of $\sim0.1\%$ light-off occurs at approximately 180\,$^\circ$C. The temperature ramp is typically continued up to 260\,$^\circ$C whereafter the temperature is decreased at the same rate as the heating ramp. After the initial light-off the sample is cooled to room temperature. When at room temperature the temperature is again increased at 3\,$^\circ$C/min until sustained oscillations occur. A typical initial treatment is seen in Figure~\ref{fgr:initial_treatment} where both the symmetrical light-off ramp and the subsequent increase in temperature to achieve sustained oscillations is seen. Often the sample will show oscillations either directly upon light-off or on the falling temperature ramp.
\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{initial_treatment.png}
  \caption{A typical example of the initial treatment of a new sample. After performing a light-off ramp where oscillations can been seen the temperature is increased to a constant value where sustained oscillations take place. The non-zero value of CO during high conversion periods is consistent with the expected QMS background signals from CO$_2$ and O$_2$.}
  \label{fgr:initial_treatment}
\end{figure}
Nanoparticles with sizes ranging from 3\,nm to 9\,nm have been tested but 3\,nm particles with a geometrical coverage of 0.1\% of the reactor area gave the most stable oscillations. No consistent dependency on oscillation frequency and duty cycle was found that could be attributed to the size of the particles.
